Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-09-22 paper-v1.tex
Design: Bounty, token.

\subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties. Bounties are a prize or monetary rewards given for completing a task before a deadline \cite{BountyGit}. Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}. Incentives can be represented by tokens, unit of values registered on a blockchain network, that represent the quantity and quality of a service within a network.
\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens. The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
Thus, the system acts also as a reputation builder.

>>>>

\subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties. Bounties are prizes or monetary rewards given for completing a task before a deadline \cite{BountyGit}. Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}. Incentives can be represented by tokens, unit of values registered on blockchain networks.
\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens. The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
Thus, the system acts also as a reputation builder.
